---
title: "Seagrass Loss"
author: "Simone Strydom, DBCA"
date: "`r Sys.time()`"
always_allow_html: yes
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    fig_width: 10
    fig_height: 6
    code_folding: show
    theme: lumen
  pdf_document: default
---

```{r setup, message=F}
if (file.exists("~/.Rprofile")) source("~/.Rprofile")
ckanr::ckanr_setup(url=Sys.getenv("CKAN_URL"), key=Sys.getenv("CKAN_API_KEY"))
library(magrittr)
library(dplyr)
library(DT)
```

# Data
Data is stored on the DBCA data catalogue.

```{r load_data}
csv_rid <- "2f7d9386-d1b2-4841-803c-4720d90bfc76"
stats <- ckanr::resource_show(csv_rid)$url %>% readr::read_csv(.)

stats %>% DT::datatable(.)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
